{\helveticaitalic{Supplementary Material}}

### 2022-02-04 tex/supplemental.tex
Split latex document into subfiles

\section{Model equations and parameters}
The asymptotic functions $m_{\infty}$ and $w_{\infty}$ for the calcium and potassium conductances, respectively, are given by
\begin{align}
  m_{\infty}(v_{i}) &= \frac{1}{2}\left(1+\tanh{\left((v_{i}-v_{A})/v_{B}\right)}\right),\\
  w_{\infty}(v_{i}) &= \frac{1}{2}\left(1+\tanh{\left((v_{i}-v_{C})/v_{D}\right)}\right).
\end{align}
Model parameters were adapted from~\cite{bose2011} and are given in \cref{tab:pars}:
\begin{table}[h]
  \caption{Default parameters for coupled Morris-Lecar model.~\label{tab:pars}}
  \centering
  \begin{tabular}{ll}
    Parameter & value\\
    \hline
              & \\
    $g_{\leak}$ & 0.15 \si{mS/cm^2}\\
    $g_{\ca}$ & 0.3 \si{mS/cm^2}\\
    $g_{\k}$ & 0.6 \si{mS/cm^2}\\
    $v_{\leak}$ & -50 mV\\
    $v_{\ca}$ & 100 mV\\
    $v_{\k}$ & -70 mV\\
    $v_{A}$ & 1 mV\\
    $v_{B}$ & 14.5 mV\\
    $v_{C}$ & 4 mV\\
    $v_{D}$ & 15 mV\\
    $I$ & 6 \si{\mu A/cm^2}\\
    $\tau$$_{w}$ & 100 ms\\
    $\tau$$_{d}$ & 1000 ms\\
    $\tau$$_{s}$ & 100 ms\\
    $v_{\theta}$ & 0 mV\\
    $v_{s}$ & -80 mV\\
    $\lambda$ & 0.5\\
    $T$ & 217 ms\\
    $\gstar$ & 0.03804 \si{mS/cm^2}\\
  \end{tabular}
\end{table}

>>>>

\section{Model equations and parameters}
The asymptotic functions $m_{\infty}$ and $w_{\infty}$ for the calcium and potassium conductances, respectively, are given by
\begin{align}
  m_{\infty}(v_{i}) &= \frac{1}{2}\left(1+\tanh{\left((v_{i}-v_{A})/v_{B}\right)}\right),\\
  w_{\infty}(v_{i}) &= \frac{1}{2}\left(1+\tanh{\left((v_{i}-v_{C})/v_{D}\right)}\right).
\end{align}
Model parameters were adapted from~\cite{bose2011} and are given in \cref{tab:pars}:
\begin{table}[h]
  \caption{Default parameters for coupled Morris-Lecar model.~\label{tab:pars}}
  \centering
  \begin{tabular}{ll}
    Parameter & value\\
    \hline
              & \\
    $g_{\leak}$ & $0.15$ \si{mS/cm^2}\\
    $g_{\ca}$ & $0.3$ \si{mS/cm^2}\\
    $g_{\k}$ & $0.6$ \si{mS/cm^2}\\
    $v_{\leak}$ & $-50$ \si{mV}\\
    $v_{\ca}$ & $100$ \si{mV}\\
    $v_{\k}$ & $-70$ \si{mV}\\
    $v_{A}$ & $1$ \si{mV}\\
    $v_{B}$ & $14.5$ \si{mV}\\
    $v_{C}$ & $4$ \si{mV}\\
    $v_{D}$ & $15$ \si{mV}\\
    $I$ & $3.8$ \si{\mu A/cm^2}\\
    $\tau_w$ & $100$ \si{ms}\\
    $\tau_a$ & $1000$ \si{ms}\\
    $\tau_b$ & $100$ \si{ms}\\
    $\tau_\kappa$ & $100$ \si{ms}\\
    $\tau_\gamma$ & $0.0001$ \si{ms}\\
    $v_{\theta}$ & $0$ \si{mV}\\
    $v_{s}$ & $-80$ \si{mV}\\
    $T$ & $376$ \si{ms}\\
    $T_{act}$ & $49$ \si{ms}\\
    $T_{inact}$ & $327$ \si{ms}\\
    $\gstar$ & $0.0036$ \si{mS/cm^2}\\
    $\lambda:=\exp(-T_{act}/\tau_b)$ & $0.612$\\
    $\rho:=\exp(-T_{inact}/\tau_a)$ & $0.721$\\
  \end{tabular}
\end{table}
